Reliable feature point matching

### 2013-08-10 text/main/ch2_background.tex
Added matching section to background

\chapter{Matching local image features}

@@

\section{A brief look at computer vision}

@@

The main difficulty lies in how the world we see around us constantly 
varies. Try for a moment to imagine that you enter a room and recognize 
the newspaper that is lying on the table, illuminated from the grey 
light coming in of the window on the opposing wall. You move across the 
room and switch on the light make out if the paper is from today, and 
then you sit down and put on your glasses to read the headline. Try to 
imagine the newspaper as you see it on three different stages. First as 
you enter the room, then as you turn after turning on the light, now 
standing on the other side of the table, and last when you are sitting 
with the paper in your hand after you put on your glasses. For each of 
these stages, picture the situation as a photography and look at how the 
newspaper changes as you move around. At first you see it at an angle 
lying in a fairly dark and grey room, the white pages reflecting the 
light from the window with a cold bluish hue and the words too far away 
to make out. Then in the second stage with light on, the object you are 
looking at has suddenly changed. When you turned on the light in the 
room, you also changed the color of the newspaper, which now has a warm 
and yellowy white color. The angle you are looking at the paper from has 
changed too, and the words and pictures are no longer upside down, 
although still slightly rotated and with the increased light in the room 
the contrast of the words and pictures of the page makes it possible for 
you to make recognize that the newspaper is from today. Finally as you 
sit down and put your glasses on the newspaper changes again. The color 
might be the same, but if you imagine taking a photography as you are 
sitting with the paper in your hand, the newspaper will look much bigger 
almost taking up the entire frame. Now that your glasses are on, the 
words stand out much clearer and you can see what is in the pictures on 
the front page.

@@

\section{Introducing local features}

@@

\section{Finding the perfect match}

Matching feature points
 - What applications require matching?
 - How is matching usually done
 - Segue into related work from paper

>>>>

\chapter{Matching Local Image Features}

@@

\section{A Brief Look at Computer Vision}

@@

\subsection{A Thought Experiment}

The main factor that makes computer vision difficult is how the world we 
see around us constantly varies. This is not something that is 
immediately obvious to the casual observer, so for the sake of clarity 
let us do a small thought experiment. Try for a moment to imagine that 
you enter a room and recognize the newspaper that is lying on the table, 
illuminated from the grey light coming in of the window on the opposing 
wall. You move across the room and switch on the light make out if the 
paper is from today, and then you sit down and put on your glasses to 
read the headline. Try to imagine the newspaper as you see it on three 
different stages. First as you enter the room, then as you turn after 
turning on the light, now standing on the other side of the table, and 
last when you are sitting with the paper in your hand after you put on 
your glasses. For each of these stages, picture the situation as a 
photography and look at how the newspaper changes as you move around. At 
first you see it at an angle lying in a fairly dark and grey room, the 
white pages reflecting the light from the window with a cold bluish hue 
and the words too far away to make out. Then in the second stage with 
light on, the object you are looking at has suddenly changed. When you 
turned on the light in the room, you also changed the color of the 
newspaper, which now has a warm and yellowy white color.  The angle you 
are looking at the paper from has changed too, and the words and 
pictures are no longer upside down, although still slightly rotated and 
with the increased light in the room the contrast of the words and 
pictures of the page makes it possible for you to make recognize that 
the newspaper is from today. Finally as you sit down and put your 
glasses on the newspaper changes again. The color might be the same, but 
if you imagine taking a photography as you are sitting with the paper in 
your hand, the newspaper will look much bigger almost taking up the 
entire frame. Now that your glasses are on, the words stand out much 
clearer and you can see what is in the pictures on the front page.

@@

\section{Introducing Local Features}

@@

\section{Finding the Perfect Match}

Most applications of feature points use them to match features across 
different images. The standard out of the box way most feature points 
are matched involve comparing the feature descriptor using some kind of 
distance measure. If we match all features of one image with all 
features of another and discard all matches that are below a certain 
threshold of similarity, we have in essence a set of matches between the
two images. For most feature points (for example SIFT and SURF), this 
similarity is measured by the cosine similarity. Binary descriptors such
as BRIEF can take advantage of the faster computation of the hamming 
distance.

\subsection{Geometric Constraints}

While the standard matching method is often computationally efficient, 
it isn't necessarily the best way to match feature points. Many matching 
methods make use of the knowledge of the position of the keypoints in 
the image, i.e.\ the geometrical meta data. Using this information can 
often yield more accurate outcomes, but they inevitably make assumptions
about the geometric relationship between the images that are being 
matched which might not hold true.

A simple example would be to only consider matches that aren't deviating 
too much with respect to the average angle and distancen as considered 
by \cite{kim2008efficient}.  This performs well in situations where no 
camera rotation occurs between the two images, but fails when this 
assumption isn't met. Various scenarios have been proposed to improve on 
this simple assumption such as epipolar constraints 
(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
Epipolar constraint carries the assumption that the two images matched 
are related by an affine transformation. That is, that there is no 
relative movement of objects in between images and either the viewpoint 
is fixed or the image resides entirely on a plane. In practice this 
assumption largely holds true when all objects we are interested in 
matching are roughly the same distance from the camera given that 
objects don't move across images.  Pairwise constraints provide a more 
robust approach to the same problem by looking at a set of proposed 
correspondences and defining a pairwise error between any two matches 
for example based on the assumption that two neighboring correspondences 
will usually have similar angles and distances. We can then convert the 
problem to an optimization problem and return a set of correspondences 
that minimizes this error such as proposed in \cite{choi2009robust} and 
\cite{leordeanu2005spectral}.  This approach provides more robustness in 
cases where assumptions that are violated globally still hold on a local 
scale.

An alternative is to pick out different areas in each image and pair 
areas when correspondence pairs are mainly found going from one area to 
another. This allows for the filtering of all correspondences that do 
not fall within paired areas. Examples include \emph{Isodata} 
\cite{das2008event}, which clusters feature points according to their 
position in the image, and the method from \cite{wu2011robust}, which 
uses maximally stable extremal regions (MSER) feature points to 
designate areas.

\subsection{Matching Without Assumptions}

In practice there are many situations where relying on the geometry of 
the image to filter correspondences is not possible, for example images 
without overlap, or adjacent objects in one image are that are separated 
in another. Furthermore, methods using geometric constraints all require 
an initial set of correspondences. If this set of correspondences can be 
narrowed down to the most probable correct matches, the geometric 
matching algorithm will benefit in terms of speed and accuracy.  Finally 
some use cases might require a speed that simply cannot be achieved by 
complex geometric methods.

In the absence of geometric constraints, only few methods are available.  
As pointed out in \cite{szeliski2010} and mentioned above, the simplest 
approach to matching feature points is to return all matches above a 
given threshold of similarity.  This can be done with a fixed threshold 
or by finding the nearest neighbors for each point (still filtering by a 
threshold to avoid including matches for feature points that have no 
counterpart in the other image).  When Lowe \cite{lowe2004sift} proposed 
the scale-invariant feature transform he included an alternative 
matching measure. Instead of rating matching by similarity assessed the 
uniqueness of a given match by looking at the two nearest neighbors of 
each feature point and calculating the matching score as the ratio of 
similarities. This method will later be referred to as \emph{Ratio}.  
Ranking the scores by their uniqueness and picking the $n$ best produces 
a set of correspondences that are distinctly matched across two images.  
Of these three methods (fixed threshold, nearest neighbors, and 
\emph{RATIO}), \emph{RATIO} was found to perform best by a slight margin 
\cite{mikolajczyk2005performance}.

%Matching feature points
% - What applications require matching?
% - How is matching usually done
% - Segue into related work from paper
